### 2021-07-06 docs/manuscript/manuscript.tex
Add ref to S3 Fig in Methods

\subsection*{Pattern formation under varying size of the morphogenetic field}
We evaluated the ability of each of the sampled GRNs to generate a striped
pattern of gene expression under varying sizes of the morphogenetic field.
Specifically, we calculated the fitness of each GRN across morphogenetic fields
composed of 10, 20, 40, and 50 cells. In these simulations we redefined the
morphogen gradient in such a way that the initial and final concentration were
constant in all the fields (\nameref{S3_Fig}A). In order to know if topologies
with the same topology had a similar fitness in the different fields, we performed
a Principal Component Analysis in Scikit-learn~0.24.2~\cite{sklearn} using the
fitness values of each in the four different fields.

>>>>

\subsection*{Pattern formation under varying size of the morphogenetic field}
We evaluated the ability of each of the sampled GRNs to generate a striped
pattern of gene expression under varying sizes of the morphogenetic field.
Specifically, we calculated the fitness of each GRN across morphogenetic fields
composed of 10, 20, 40, and 50 cells. In these simulations we redefined the
morphogen gradient in such a way that the initial and final concentration were
constant in all the fields (\nameref{S3_Fig}A). In order to know if topologies
with the same topology had a similar fitness in the different fields, we performed
a Principal Component Analysis in Scikit-learn~0.24.2~\cite{sklearn} using the
fitness values of each in the four different fields (see \nameref{S3_Fig}).
